## Week1-2
#### Goal: To integrate two data frames concerning the number and nationality of tourists leaving for Taiwan, as well as the number of Taiwanese tourists and their destination.
#### Data Source:
#### -https://data.gov.tw/dataset/7325
#### -https://data.gov.tw/dataset/45537

### Step1:Import data
```{r}
library(dplyr)
library(readxl)
Foreignernation <-read_excel("C:\\Users\\User\\Desktop\\Foreigner_nation.xlsx")
Taiwanesedestination <- read_excel("C:\\Users\\User\\Desktop\\Taiwanese_destination (2).xlsx")
head(Taiwanesedestination)
head(Foreignernation)
```
### Step2: Use `select()` and `slice()` to set up the range of countries and years.
```{r}
Foreignernation1<- slice( Foreignernation, 1,2,5,6,7,8,9,10)
Foreignernation2<- select( Foreignernation1,2,13,14,15,16,17)
head(Foreignernation2)
Taiwanesedestination1 <- slice( Taiwanesedestination, 3,4,6,5,9,8,7,11 )
Taiwanesedestination2 <- select( Taiwanesedestination1, 2,13,14,15,16,17)
head(Taiwanesedestination2)
```
### Step3: Use `names()` to rename the name of column
### (FT=Foreign Tourist / TT=Taiwanese Tourist)
```{r}
names(Foreignernation2)[names(Foreignernation2)=="2012"]<-"2012_FT"
names(Foreignernation2)[names(Foreignernation2)=="2013"]<-"2013_FT"
names(Foreignernation2)[names(Foreignernation2)=="2014"]<-"2014_FT"
names(Foreignernation2)[names(Foreignernation2)=="2015"]<-"2015_FT"
names(Foreignernation2)[names(Foreignernation2)=="2016"]<-"2016_FT"
names(Taiwanesedestination2)[names(Taiwanesedestination2)=="2012"]<-"2012_TT"
names(Taiwanesedestination2)[names(Taiwanesedestination2)=="2013"]<-"2013_TT"
names(Taiwanesedestination2)[names(Taiwanesedestination2)=="2014"]<-"2014_TT"
names(Taiwanesedestination2)[names(Taiwanesedestination2)=="2015"]<-"2015_TT"
names(Taiwanesedestination2)[names(Taiwanesedestination2)=="2016"]<-"2016_TT"
head(Foreignernation2)
head(Taiwanesedestination2)
```
### Step4: Integrate two data frames with `cbind()`, then delete the "country" column by assigning it to `NULL`.
```{r}
Comparison <- cbind(Foreignernation2, Taiwanesedestination2)
Comparison$country = NULL
head(Comparison)
```

